Gut-resident microorganisms and their genes are associated with cognition and neuroanatomy in children

### 2023-03-31 manuscript/main.tex
Guilherme comments

\begin{sidewaysfigure}[!htb]
    \centering
    \includegraphics[width=\textwidth]{assets/Figure3.png}
    \caption{
        Random forest models predict concurrently measured cognitive function.
        Comparison of RF predictor importance versus linear models for children
        between birth and 6 months old (\textbf{A}), and for those older than 18 months
        (\textbf{B}). Colors represent whether the species belong to the group of
        top-important features that account for 80\% of the cumulative
        importance on the RF model, if that species was significant (q
        \textless{} 0.2) in linear models, both, or neither. Ranked feature
        importance for taxa in RF models for children between birth and 6 months
        old (\textbf{C}), and for those older than 18 months (\textbf{D}). Taxa that are important
        for RF models both for children under 6 months and for those over 18
        months (\textbf{E}), only for children under 6 months (\textbf{F}), and only for children
        over 18 months (\textbf{G})
    }
    \label{fig:3}
\end{sidewaysfigure}

@@

As with LMs, RF models for children under 6 months old
performed poorly (mean test-set correlation -0.12, mean RMSE 12.70),
but RFs were consistently able to learn the relationship between taxa
and cognitive function scores in children over 18 months of age (mean
test-set correlation 0.429, mean RMSE 17.29). For both age groups,
species that were important in RF overlapped with those that were
significant when testing the relationship with LMs (Figure
3A-B, Table S1A-B); except for \emph{Eubacterium ramulus},
all taxa that were significant using LMs belonged to a group
responsible for 80\% of the total importance in RF models
(Table 3, Figure 3A).
However, the rank-ordering of LM significance and RF importance
had substantive differences. For example, in children under 6 months,
only \emph{B. wexlerae} was significantly associated with cognitive function in LMs, but
was ranked 20th in importance for RF models.

>>>>

\begin{sidewaysfigure}[!htb]
    \centering
    \includegraphics[width=\textwidth]{assets/Figure3.png}
    \caption{
        Random forest models predict concurrently measured cognitive function.
        Comparison of RF predictor importance versus linear models for children
        between birth and 6 months old (\textbf{A}), and for those older than 18 months
        (\textbf{B}). Colors represent whether the species belong to the group of
        top-important features that account for 60\% of the cumulative
        importance on the RF model, if that species was significant (q
        \textless{} 0.2) in linear models, both, or neither. Ranked feature
        importance for taxa in RF models for children between birth and 6 months
        old (\textbf{C}), and for those older than 18 months (\textbf{D}). Taxa that are important
        for RF models both for children under 6 months and for those over 18
        months (\textbf{E}), only for children under 6 months (\textbf{F}), and only for children
        over 18 months (\textbf{G})
    }
    \label{fig:3}
\end{sidewaysfigure}

@@

As with LMs, RF models for children under 6 months old
performed poorly (mean test-set correlation -0.12, mean RMSE 12.70),
but RFs were consistently able to learn the relationship between taxa
and cognitive function scores in children over 18 months of age (mean
test-set correlation 0.429, mean RMSE 17.29). For both age groups,
species that were important in RF overlapped with those that were
significant when testing the relationship with LMs (Figure
3A-B, Table S1A-B); except for \emph{Eubacterium ramulus},
all taxa that were significant using LMs belonged to a group
responsible for 60\% of the total importance in RF models
(Table 3, Figure 3A).
However, the rank-ordering of LM significance and RF importance
had substantive differences. For example, in children under 6 months,
only \emph{B. wexlerae} was significantly associated with cognitive function in LMs, but
was ranked 20th in importance for RF models.
